Supplementary Materials

### 2018-03-27 paper/appendix_modelDescription.tex

The Decomposable Attention model is an end-to-end model that takes vectorized premise sentence and hypothesis sentence, and output a probability distribution over three labels. The pipeline can be separated into three phases: encoder, attention and classifier. Here we briefly formalize these three layers.

\subsection{Encoder}
Denote the premise sentence as $\overline{\boldsymbol{P}} = (\overline{\boldsymbol{p}}_1, \overline{\boldsymbol{p}}_2, ..., \overline{\boldsymbol{p}}_m)$ and hypothesis sentence as $\overline{\boldsymbol{H}} = (\overline{\boldsymbol{h}}_1, \overline{\boldsymbol{h}}_2, ..., \overline{\boldsymbol{h}}_n)$ where $\overline{\boldsymbol{p}}_i$ and $\overline{\boldsymbol{h}}_j$ are the input embedding vectors respectively. The purpose of encoder is to generate specialized encodings that will participate in the following steps of the model. Define the encoder function as
\begin{align}
  \boldsymbol{P} &= F(\overline{\boldsymbol{P}})\\
  \boldsymbol{H} &= F(\overline{\boldsymbol{H}})
\end{align}

@@

where G is the aggregation layer (e.g. two-layer ReLU) and $[\cdot|\cdot]$ denotes concatenation. Notice this aggregation layer jointly considers embeddings, encodings and attentions. With the aggregated premise feature $\boldsymbol{u}_i$ and hypothesis feature $\boldsymbol{v}_j$, the classifier does further feature conjunction to predict weight on each entailment score:
\begin{align}
  \boldsymbol{y} &= Z([\sum_i \boldsymbol{u}_i | \sum_j \boldsymbol{v}_j]) \label{eq:yscore}
\end{align}

@@

\textbf{Comment} We used the same network setting in the Decomposable Attention paper~\cite{parikh2016emnlp}. That are, network hidden size is $200$; input word embeddings are $200$ embeddings (downsampled from $300$ dimensional GloVe embeddings~\cite{PenningtonSocherManning2014} by a learnable linear layer); dropout~\cite{SrivastavaHinton2014} is $0.2$ for learning; and learning rate is $0.05$.

>>>>

The Decomposable Attention~\cite{parikh2016emnlp} model is an end-to-end model that takes vectorized premise sentence and hypothesis sentence, and output a probability distribution over three labels. The pipeline can be separated into three phases: encoder, attention and classifier. Here we briefly formalize these three layers.

\subsection{Encoder}
Denote the premise sentence as $\overline{\boldsymbol{P}} = (\overline{\boldsymbol{p}}_1, \overline{\boldsymbol{p}}_2, ..., \overline{\boldsymbol{p}}_m)$ and hypothesis sentence as $\overline{\boldsymbol{H}} = (\overline{\boldsymbol{h}}_1, \overline{\boldsymbol{h}}_2, ..., \overline{\boldsymbol{h}}_n)$ where $\overline{\boldsymbol{p}}_i$ and $\overline{\boldsymbol{h}}_j$ are the input embedding vectors respectively. The purpose of encoder is to generate specialized encodings for attention. Define the encoder function as
\begin{align}
  \boldsymbol{P} &= F(\overline{\boldsymbol{P}})\\
  \boldsymbol{H} &= F(\overline{\boldsymbol{H}})
\end{align}

@@

where G is the aggregation layer (e.g. two-layer ReLU) and $[\cdot|\cdot]$ denotes concatenation. With the aggregated premise feature $\boldsymbol{u}_i$ and hypothesis feature $\boldsymbol{v}_j$, the classifier does further feature conjunction to predict weight on each entailment score:
\begin{align}
  \boldsymbol{y} &= Z([\sum_i \boldsymbol{u}_i | \sum_j \boldsymbol{v}_j]) \label{eq:yscore}
\end{align}

@@

\textbf{Comment} We adopted the same network setting in the Decomposable Attention paper~\cite{parikh2016emnlp}. That are, network hidden size is $200$; input word embeddings are $200$d embeddings (downsampled from $300$d GloVe embeddings~\cite{PenningtonSocherManning2014} by a learnable linear layer). For learning, dropout~\cite{SrivastavaHinton2014} is $0.2$ and learning rate is $0.05$. Optimization algorithm is AdaGrad~\cite{duchi2011adaptive} with mini-batch size 64 and number of epochs 300.
